18th International Satisfiability Modulo Theories Competition (SMT-COMP 2023): Rules and Procedures

### 2023-04-26 rules/rules23.tex
Model validation plus form link

  \item {\bf \mvaltrack.}  \emergencystretch.5cm Last year's
    competition introduced the experimental divisions QF\_FPArith
    (excluding the logics QF\_ABVFP, QF\_AUFBVFP, and QF\_ABVFPLRA).
  %
  This year these divisions will no longer be experimental.
  %
  In addition, we add this year the new experimental division for
  non-linear arithmetic and for datatypes.  These include the divisions
  QF\_NonLinearIntArith, QF\_NonLinearRealArith,
  QF\_Equality+NonLinearArithm,
  and QF\_Datatypes
  (excluding all logics involving Arrays).  \todo{root-obj,
    partially defined functions}
%
  \rationale{Last year's divisions ran successfully, so there
    is no reason to keep them experimental.
    %
    For the new divisions, as before, given the inconsistencies across different
    model producing solvers, we proceed in an experimental fashion to push for
    model standardization. We exclude logics containing arrays since
    there is no standardized way of expressing array model values and
    we do not want to add too many new logics.}

@@

\header{Participation in the Competition.}
%
For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available, or communicated separately to the
organisers for the \cloudtrack{} and \paralleltrack{}.  StarExec
supports solver configurations.  You can have at most one configuration
for each track (named after the track) and a default configuration used
for tracks without a track-specific configuration.
Moreover, the organizers must be informed of the solver's presence
\emph{and the tracks and divisions which it enters} via the web form
at \todo{Needs to be updated!}
\begin{center}
  \url{https://forms.gle/ewNQdFJbmQ12GxpX8}
\end{center}
For each track the submission must specify the logics which are
supported by the solver.  The solver will enter all divisions where it
supports at least one logic.  A submission \textbf{must} also include a
link to the \emph{system description} (see below) and a \emph{32-bit
  unsigned integer}.  These integer numbers, collected from all
submissions, are used to seed competition tools.

@@

\header{Benchmark Selection.}  This track has the divisions QF\_Bitvec,
QF\_LinearIntArith, QF\_LinearReal\-Arith, QF\_Equality (only with QF\_UF
benchmarks), QF\_Equality+LinearArith (only with QF\_UFIDL, QF\_UFLIA, and
QF\_UFLRA benchmarks), and QF\_Equality+Bitvec (only with QF\_UFBV benchmarks).
%
This year all divisions with UF logics (with uninterpreted functions) are
experimental divisions.
%
The track will run on a
selection of non-incremental \emph{sat} benchmarks from these
logics (as described on page~\pageref{benchmark-selection}).
%
We exclude from the selection all benchmarks containing arrays or datatypes.

@@

>>>>

  \item {\bf \mvaltrack.}  \emergencystretch.5cm Last year's
    competition introduced the experimental divisions QF\_FPArith
    (excluding the logics QF\_ABVFP, QF\_AUFBVFP, and QF\_ABVFPLRA).
  %
  This year these divisions will no longer be experimental.
  %
  In addition, we add this year the new experimental division for
  arrays, non-linear arithmetic and for datatypes.  These include the divisions
  QF\_NonLinearIntArith, QF\_NonLinearRealArith,
  QF\_Equality+NonLinearArithm,
  and QF\_Datatypes.
%
  \rationale{Last year's divisions ran successfully, so there
    is no reason to keep them experimental.
    %
    For the new divisions, as before, given the inconsistencies across different
    model producing solvers, we proceed in an experimental fashion to push for
    model standardization. We exclude logics containing arrays since
    there is no standardized way of expressing array model values and
    we do not want to add too many new logics.}

@@

\header{Participation in the Competition.}
%
For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available, or communicated separately to the
organisers for the \cloudtrack{} and \paralleltrack{}.  StarExec
supports solver configurations.  You can have at most one configuration
for each track (named after the track) and a default configuration used
for tracks without a track-specific configuration.
Moreover, the organizers must be informed of the solver's presence
\emph{and the tracks and divisions which it enters} via the web form
at
\begin{center}
  \url{https://forms.gle/xhUDQaTynbS3mccE7}
\end{center}
For each track the submission must specify the logics which are
supported by the solver.  The solver will enter all divisions where it
supports at least one logic.  A submission \textbf{must} also include a
link to the \emph{system description} (see below) and a \emph{32-bit
  unsigned integer}.  These integer numbers, collected from all
submissions, are used to seed competition tools.

@@

\header{Benchmark Selection.}  This track has the divisions QF\_Bitvec,
QF\_DataTypes, QF\_Equality,
QF\_Equality+Bitvec,
QF\_Equality+(Non)LinearArith,  
QF\_(Non)LinearIntArith, and QF\_(Non)\-LinearRealArith.
%
This year all divisions with non-linear arithmetic, arrays, and data
types are experimental divisions.
%
The track will run on a
selection of non-incremental \emph{sat} benchmarks from these
logics (as described on page~\pageref{benchmark-selection}).
%
We exclude from the selection all benchmarks containing arrays or datatypes.

@@

The new experimental divisions require additional syntax to represent
their models.  We propose the new syntax on the SMT-COMP website
{\url{https://smt-comp.github.io/2023/model.html}}.
